An Abstraction-based Approach to Network Synthesis

### 2016-10-27 paper/abstraction/paper.tex
adding inference rules
edits to section 2

\newcommand{\sysname}{{\small \sf Propane}\xspace}

@@

>>>>

\newcommand{\sysname}{{\small \sf Methane}\xspace}

@@

We motivate \sysname using an example data center network adapted from prior work~\cite{propane}. Our network, shown in Figure~\ref{fig:example}, is a standard folded-Clos topology with four pods. It has eight top-of-rack (ToR) switches, T[1--8]; eight aggregation switches, A[1--8]; and two spine switches, S[1--2]. Groups of addresses, P[1--8], are for services hosted in each rack. Such groups are called address {\em prefixes} because they are compactly encoded using the common prefix that addresses share.

The figure also shows the intended policy. Internal connectivity should be complete, i.e., all nodes must be able to talk to each other. Pods 1 and 2 host services that are meant to be globally accessible and thus their addresses should be announced externally, but only after the individual prefixes P[1--4] are aggregated into a single prefix PG. Finally, pods 3 and 4 host services that are not meant to be externally visible and thus their address should not be announced externally.

To correctly configure the policy above, the network engineer's task is to generate low-level configuration commands for each switch in the network. This implies making sure, for instance, that all switch interfaces are assigned correct addresses; all routing adjacencies are correctly configured (e.g., T1's configuration includes A1 as neighbor and vice-versa); all switches announce their own addresses (so that they can be reached for management purposes) and the ToRs announce the correct prefixes for their services; all switches  forward the prefix announcements that they should to each neighbor and not forward those that they should not (e.g., the spines should forward prefixes for local services to internal neighbors but not external neighbors); and the spines announce externally only the aggregate global prefix. As many have observed before, such configuration tasks are highly challenging and, consequently, configuration errors are the leading contributor to network outages~\cite{x,y,z,batfish,propane}.

To reduce errors, network engineers are moving toward a template-based approach. Here, instead of authoring one configuration file per router, they author one configuration template per {\em role}, where each role is played by one or more routers.\footnote{If a role is played by devices from different vendors, there is one template per role-vendor combination because templates use vendor configuration language.} For instance, the network in Figure~\ref{fig:example} has five roles: spine, global aggregator, global ToR, local aggregator, and local ToR. Role templates have parameters for various aspects of the configuration (e.g., interface addresses, list of neighbors), and they are compiled to device configurations by instantiating the parameters using a database that stores parameter values for each device.

Templates provide two key advantages. First, they help eliminate a class of configuration errors that stem from typos and inconsistencies, e.g., using the wrong address for a switch, having inconsistent addresses for the two ends of a link, and failing to configure one side of a routing adjacency.  Second, template design work can be re-used when the topology changes while maintaining its basic structure (e.g., adding a new pod to the data center) or multiple networks with similar structures need to be instantiated (e.g., in an organization that runs multiple data centers).

%Second, the engineers need to author and reason about fewer independent ``files"---18 versus 5 in our example but the ratio can be multiple orders of magnitude for large networks.

Today's templates, however, are far from perfect. While they reduce a class of errors, they do not help with deeper, logical bugs.
%, e.g., incorrect strategy for determining how announcements to a neighbor are forwarded
%, not realizing when or where aggregation should be used, 
%and not understanding the interaction between configuration commands. 
To author correct templates, engineers must still do themselves the conceptually challenging task of breaking down complex, global policies into role templates such that the collective behavior of the templates (upon compilation to configurations) correctly implements the policy under all failure conditions.

As a result, the types of configuration design errors in our example network pointed in prior work~\cite{propane} can occur in template design as well. For instance, to keep local prefixes internal the engineer may implement announcement forwarding on spines based on the identity of the neighbor, i.e., do not announce externally anything heard from local aggregators. This implementation works correctly when there are no failures but local prefixes can leak to the outside world when failures disconnect a spine from both aggregators in a local pod. Specifically, when S1 is disconnected from A5 and A6, it may hear about P5 and P6 from A3 and A4 (via A[5--6]->S2->A[3--4]), and it will then announce those prefixes outside (since they no not come from a local aggregator), leading to a policy violation. A correct implementation here would be for each spine to not advertise externally announcements from local aggregators {\em and} reject announcements that have traversed the other spine.

Lacking correctness guarantees, some engineers use simulations to gain confidence that their templates correctly implement policy under a range of failure cases (e.g., all combinations of two link failures), but for large networks these simulations tend to be highly expensive and still do not provide any guarantees beyond the tested cases. Further, that simulations over a concrete topology is the basis for checking correctness means that templates cannot be directly re-used when the topology evolves or on another similarly-structured topology.

Templates that work for a given concrete topology may not work for minor variations of the topology.
